Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-07-08 paper/paper.tex
misc

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\setcopyright{acmlicensed} %TODO
\acmPrice{}
\acmDOI{10.1145/3236800}
\acmYear{2018}
\copyrightyear{2018}
\acmJournal{PACMPL}
\acmVolume{2}
\acmNumber{ICFP}
\acmArticle{105}
\acmMonth{9}

@@

\begin{lstlisting}
  def drive(todo: List[State], seen: Set[State]): Set[State] = todo match {
    case Nil => seen
    case hd::tl if seen.contains(hd) => drive(tl, seen)
    case hd::tl => drive(step(hd).toList ++ tl, seen + hd)
  }
  def analyze(e: Expr): Set[State] = drive(List(inject(e)), Set())
\end{lstlisting}

@@

Function @f1@ and @f2@ mutually invoke each other, so the frames of @f1@ and @f@ will be
alternately pushed onto the top of the current stack. However, no two existing stack
components are identical in the state space. One can decide the reachability of a state
through Dyck state graph \cite{earl2010pushdown, earl2012introspective}, but simply
caching the explored states (i.e., @seen@) would not always make the analyzer terminate.

@@

Function @ndcontinue@ is identical to the dispatching logic in @continue@ when @konts@ is empty,
except that the first application of @drive_step@ is reduced to @ndcontinue@ (we can safely do this because 
@ae@ is atomic and @knots@ is empty).
When @ndk@ is empty, the current set of explored states @seen@ is returned, after which the analysis terminates.
Otherwise, a new @NDState@ is constructed depending on the status of the closures set.

@@

The circular meta-continuation is abstracted by the @nd@ operator, and only one continuation
remains at the level of @aeval@. 
When encountering a set of possible closures, we apply @nd@ on the set with the latest explored
configurations and an anonymous function that works on each closure. The beginning part 
(before calling @aeval@) of this anonymous function is essentially abstracted from @makeMCont@, 
which constructs new environment and store for the closure being evaluated.
Then we apply @aeval@ on the body expression of the closure with a continuation, 
which is inlined from @new_cont@ and will invoke @aeval@ on @e@ with the current continuation of the @let@ expression.

>>>>

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\setcopyright{rightsretained}
\acmPrice{}
\acmDOI{10.1145/3236800}
\acmYear{2018}
\copyrightyear{2018}
\acmJournal{PACMPL}
\acmVolume{2}
\acmNumber{ICFP}
\acmArticle{105}
\acmMonth{9}

@@

\begin{lstlisting}
  def drive(todo: List[State], seen: Set[State]): Set[State] = todo match {
    case Nil => seen
    case hd::tl if seen.contains(hd) => drive(tl, seen)
    case hd::tl => drive(step(hd) ++ tl, seen + hd)
  }
  def analyze(e: Expr): Set[State] = drive(List(inject(e)), Set())
\end{lstlisting}

@@

Function @f1@ and @f2@ mutually invoke each other, so the frames of @f1@ and @f2@ will be
alternately pushed onto the top of the current stack. However, no two existing stack
components are identical in the state space. One can decide the reachability of a state
through Dyck state graph \cite{earl2010pushdown, earl2012introspective}, but simply
caching the explored states (i.e., @seen@) would not always make the analyzer terminate.

@@

Function @ndcontinue@ is identical to the foregoing dispatching logic of meta-continuations when @konts@ is empty,
except that the first application of @drive_step@ is reduced to @ndcontinue@ (we can safely do this because 
@ae@ is atomic and @knots@ is empty).
When @ndk@ is empty, the current set of explored states @seen@ is returned, after which the analysis terminates.
Otherwise, a new @NDState@ is constructed depending on the status of the closures set.

@@

The circular meta-continuation is abstracted by the @nd@ operator, and only one continuation
remains at the level of @aeval@. 
When encountering a set of possible closures, we apply @nd@ on the set with the latest explored
configurations and an anonymous function that works on each closure. The beginning part 
(before calling @aeval@) of this anonymous function is essentially abstracted from @makeMCont@, 
which constructs new environment and store for the closure being evaluated.
Then we apply @aeval@ on the body expression of the closure with a continuation, 
which is inlined from @new_cont@ and will apply @aeval@ to @e@ with the current continuation of the @let@ expression.
